Kinematics of the Palomar 5 stellar stream from RR Lyrae stars

### 2019-09-03 paper/main.tex
Updates from Overleaf

% TODO:
% - Check whether I use p > 0.01 or p > 0.1 for sky plot figure
% - Over-plot the sky track borders on MSTO plot
% - Add PM and distance dispersion as parameters to fit, or cite out to the values I fix them to
% - Compute the autocorrelation time for emcee instead, thin by the acor length

@@

\begin{figure*}[t]
\begin{center}
\includegraphics[width=\textwidth]{members.pdf}
\caption{Sky positions of RRLs with Pal 5 membership probabilities $>0.01$ \todo{CM: APW check this number, I think it might be 0.1?}, colored by membership probability (markers). The background greyscale shows the surface density of CMD-filtered main sequence stars from \citet{Bonaca:2019}. Note that the membership probability does not incorporate sky position information, but a clear over-density of high-probability RRL members do trace the stream on the sky.}
\label{fig:members}
\end{center}
\end{figure*}

@@

\subsection{RRLs associated with Pal 5 and its tails}
%SP: changed RR Lyrae stars to RR Lyra stars a few places, maybe check whole manuscript (otherwise plural twice).
%CM: Sarah, I see your point, but I've never seen it written like that in the literature. Anyway, since we're using RRLs as an abbreviation, I've changed all instances to this in the whole manuscript.
We find a total of 24 RRLs with membership probability $> 0.5$ that lie within $1\degr$ of the stream track \citep[again using the track from][]{Bonaca:2019}.
Of those, 13 are classified as type \typeab\ and 11 are classified as type \typec\ RRLs.
We find a total of 9 RRLs within the estimated Jacobi radius of the cluster ($\approx 12'$), meaning that 15 RRLs are spread between the leading and trailing tails.
\figurename~\ref{fig:members} shows the sky positions of all RRLs with membership probability $>0.01$ over-plotted on the density of filtered main sequence stars from \citet{Bonaca:2019}.
We note that there are a few RRLs outside of the main stream track that appear to be at a consistent distance with consistent proper motions (e.g., the two stars near $\alpha = 230\degr$, $\delta = 0\degr$ in \figurename~\ref{fig:members}) that are not included in the tally above.
No theoretical models of Pal 5 have predicted tidal debris at such locations, so follow-up spectroscopy to confirm or rule out their origin would be very informative.

>>>>

% TODO:
% - Check whether I use p > 0.01 or p > 0.1 for sky plot figure
% - Over-plot the sky track borders on MSTO plot
% - Add PM and distance dispersion as parameters to fit, or cite out to the values I fix them to
%     - APW: I tried running with these as parameters, but they are unconstrained, so doesn't help. I'll just set the dispersions to small (<uncertainties) values and explain.
% - Compute the autocorrelation time for emcee instead, thin by the acor length

@@

\begin{figure*}[t]
\begin{center}
\includegraphics[width=\textwidth]{members.pdf}
\caption{Sky positions of RRLs with Pal 5 membership probabilities $>0.1$, colored by membership probability (markers). The background greyscale shows the surface density of CMD-filtered main sequence stars from \citet{Bonaca:2019}. Note that the membership probability does not incorporate sky position information, but a clear over-density of high-probability RRL members do trace the stream on the sky.}
\label{fig:members}
\end{center}
\end{figure*}

@@

\subsection{RRLs associated with Pal 5 and its tails}
%SP: changed RR Lyrae stars to RR Lyra stars a few places, maybe check whole manuscript (otherwise plural twice).
%CM: Sarah, I see your point, but I've never seen it written like that in the literature. Anyway, since we're using RRLs as an abbreviation, I've changed all instances to this in the whole manuscript.
We find a total of 24 RRLs with membership probability $> 0.5$ that lie within $1\degr$ of the stream track \citep[again using the track from][]{Bonaca:2019}.
Of those, 13 are classified as type \typeab\ and 11 are classified as type \typec\ RRLs.
We find a total of 9 RRLs within the estimated Jacobi radius of the cluster ($\approx 12'$), meaning that 15 RRLs are spread between the leading and trailing tails.
\figurename~\ref{fig:members} shows the sky positions of all RRLs with membership probability $>0.1$ over-plotted on the density of filtered main sequence stars from \citet{Bonaca:2019}.
We note that there are a few RRLs outside of the main stream track that appear to be at a consistent distance with consistent proper motions (e.g., the two stars near $\alpha = 230\degr$, $\delta = 0\degr$ in \figurename~\ref{fig:members}) that are not included in the tally above.
No theoretical models of Pal 5 have predicted tidal debris at such locations, so follow-up spectroscopy to confirm or rule out their origin would be very informative.
